---
title: "Final Stability Summary Across Prompts"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(readr)
library(dplyr)
library(knitr)
library(purrr)
```

## Overview

This report summarizes stability across the 19 prompts for each covariate group.

- Overall mean = average of prompt-level `mean_stability_score`
- Overall SD = standard deviation of prompt-level `mean_stability_score` (variation in consistency across prompts)

```{r final-summary}
knit_input <- tryCatch(knitr::current_input(), error = function(e) "")
knit_dir <- if (is.character(knit_input) && length(knit_input) == 1 && nzchar(knit_input)) {
  dirname(knit_input)
} else {
  ""
}

candidate_dirs <- c(
  ".",
  "clean_responses/stability_summary",
  "experiment_data/consistency/clean_responses/stability_summary",
  file.path(knit_dir, "clean_responses", "stability_summary"),
  file.path(dirname(knit_dir), "clean_responses", "stability_summary"),
  knit_dir
)
candidate_dirs <- unique(candidate_dirs[nzchar(candidate_dirs)])

summary_probe <- "all_covariates_stability_summary.csv"
base_dir <- candidate_dirs[
  which(file.exists(file.path(candidate_dirs, summary_probe)))[1]
]

if (is.na(base_dir)) {
  stop(
    paste0(
      "Could not locate summary CSV files. Checked: ",
      paste(candidate_dirs, collapse = " | ")
    )
  )
}

summary_files <- tibble::tribble(
  ~covariate_group, ~file_name,
  "all_covariates", "all_covariates_stability_summary.csv",
  "demo_covariates", "demo_covariates_stability_summary.csv",
  "family_covariates", "family_covariates_stability_summary.csv",
  "ses_covariates", "ses_covariates_stability_summary.csv"
)

final_summary <- purrr::pmap_dfr(
  summary_files,
  function(covariate_group, file_name) {
    data <- read_csv(file.path(base_dir, file_name), show_col_types = FALSE)
    tibble(
      covariate_group = covariate_group,
      n_prompts = nrow(data),
      overall_mean = mean(data$mean_stability_score, na.rm = TRUE),
      overall_sd = sd(data$mean_stability_score, na.rm = TRUE)
    )
  }
) %>%
  mutate(
    overall_mean = round(overall_mean, 4),
    overall_sd = round(overall_sd, 4)
  )

kable(
  final_summary,
  col.names = c("Covariate Group", "Prompts", "Overall Mean", "Overall SD"),
  caption = "Final stability summary across prompts"
)
```

## Summary Interpretation

The **overall mean** summarizes average stability across prompts for each covariate group. Higher values indicate more consistent responses overall. The **overall SD** summarizes how much stability changes from one prompt to another within that group. Lower SD means consistency is more uniform across prompts.

```{r summary-interpretation, results='asis'}
ranked_mean <- final_summary %>% arrange(desc(overall_mean))
ranked_sd <- final_summary %>% arrange(overall_sd)

best_mean <- ranked_mean %>% slice(1)
worst_mean <- ranked_mean %>% slice(n())
most_uniform <- ranked_sd %>% slice(1)
least_uniform <- ranked_sd %>% slice(n())

cat(
  paste0(
    "- Highest average stability: **", best_mean$covariate_group, "** (Mean = ",
    sprintf("%.4f", best_mean$overall_mean), ", SD = ", sprintf("%.4f", best_mean$overall_sd), ").\n",
    "- Lowest average stability: **", worst_mean$covariate_group, "** (Mean = ",
    sprintf("%.4f", worst_mean$overall_mean), ", SD = ", sprintf("%.4f", worst_mean$overall_sd), ").\n",
    "- Most uniform across prompts (lowest SD): **", most_uniform$covariate_group, "** (SD = ",
    sprintf("%.4f", most_uniform$overall_sd), ").\n",
    "- Least uniform across prompts (highest SD): **", least_uniform$covariate_group, "** (SD = ",
    sprintf("%.4f", least_uniform$overall_sd), ").\n"
  )
)

cat("\nOverall ranking by mean stability:\n")
for (i in seq_len(nrow(ranked_mean))) {
  cat(
    paste0(
      i, ". **", ranked_mean$covariate_group[i], "**: Mean = ",
      sprintf("%.4f", ranked_mean$overall_mean[i]),
      ", SD = ", sprintf("%.4f", ranked_mean$overall_sd[i]), "\n"
    )
  )
}
```
